Self-test EPR pair with constant alphabet

### 2018-12-11 Draft/draft.tex
Honghao: finished introducing components of the whole game

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}[1]{\sigma_x^{(#1)}}
\newcommand{\pauliz}[1]{\sigma_z^{(#1)}}
\newcommand{\G}[1]{G^{(#1)}}
\newcommand{\LS}{LS}

@@

The main tool to understand linear system game is through its solution group over $\Z_d$.
\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
	\begin{align}
		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
	\end{align}
	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
	\begin{align}
		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
	\end{align}
	Then the solution group has presentation 
	\begin{align}
	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
	\end{align}
\end{definition}
Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
\begin{definition}[Operator solution]
	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
	representation mapping $\J$ to $\overline{\omega_d}\1$.
\end{definition}
What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
linear system game from its operator solution and vice versa.
%========================================
\section{Components of $\G{d}$}
%========================================
%----------------------------------------------------------------
\subsection{The linear system game}
%----------------------------------------------------------------
The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is an embedding of the qudit Pauli group,
which is defined as
\begin{align}
	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
\end{align}
To construct $\LS$, we introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
by the following relations
\begin{align}
\label{eq:sim}
	u_x x u_x = x^2, \quad
	u_z z u_z = z^2.
\end{align}
Such relations give us the freedom to use the same solution group to embed different $\Pg_d$.

With constraints imposed by other components of the whole game, the two conditions above 
imply that the eigenvalues of $x$ and $z$ are $\{\omega_d^k = e^{ik\pi/d}\}_{k=1}^d$ with $d$ odd, prime and
$\Z/(d\Z)$ has primitive root $2$ and the eigenspaces for different eigenvalues are of the same dimension.
\hl{Later we will set the exponent to be $a \in \{2, 3, 5\}$ which is the primitive root of infinitely many prime numbers and
construct a nonlocal game that can self-test infinitely many maximally entangled state.}
\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}

Secondly, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
relation $xzx^{-1}z^{-1} = \J$.

It can be easily checked that the qudit Pauli-x and Pauli-z operators of dimension $d$ satisfy the new relations 
above, where Pauli-x and Pauli-z operators are defined by
\begin{align}
	\sigma_x = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
	\sigma_z = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
\end{align}
Moreover, if $U_x\sigma_xU_x^\dagger = \sigma_x^2$ and $U_z\sigma_zU_z^\dagger = \sigma_z^2$,
we can verify that 
\begin{align}
	U_xU_z = \1 = U_zU_x,
\end{align}
Hence, we define the new group by
\begin{equation}
\begin{aligned}
	\Pg =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
\end{aligned}
\end{equation}
\hl{Since $\Pg_d$'s relations satisfy the relations of $\Pg$, can we say $\Pg_d$ is a subgroup of $\Pg$?}
This group will be embedded in a solution group, $\Gamma_\Pg$, following Slofstra's embedding techniques.
See Appendix~\ref{sec:construct} for details.
\bibliographystyle{alphaurl}
\bibliography{quantum_correlation}
\appendix
%========================================
\section{Proof of \cref{thm:selftest} }
\label{sec:selftest}
%========================================
\begin{proof}
Following the techniques developed in Ref.~\cite{bamps2015}, the first step is to find a sum-of-square decomposition of 
\begin{align}
	\bar{\I}_\alpha = 2\sqrt{\alpha^2+1} \1 - \I_\alpha
	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(A_0B_0+A_0B_1) -  A_1B_0 + A_1B_1.
\end{align} 
With the following notation
\begin{align*}
	Z_A = A_0 &\quad X_A = A_1\\
	Z_B = \frac{B_0+B_1}{2\cos(\mu)} &\quad X_B = \frac{B_0-B_1}{2\sin(\mu)},
\end{align*}
the two SOS decompositions that we use are
\begin{align}
	\label{eq:sos1}&\bar{\I}_\alpha = \frac{\sin(\mu)\bar{\I}_\alpha^2 + 4\sin(\mu)\cos(\mu)^2(Z_AX_B+X_AZ_B)^2}{4},\\
	\label{eq:sos2}&\bar{\I}_\alpha = \frac{\cos^2(\mu)}{\sin(\mu)}(Z_A-Z_B)^2 + \sin(\mu) (X_A-X_B)^2.
\end{align}
The verification is omitted here.

>>>>

% Table with multi-row
\usepackage{multirow}

@@

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{EPR^{(#1)}}
\newcommand{\paulix}[1]{\sigma_x^{(#1)}}
\newcommand{\pauliz}[1]{\sigma_z^{(#1)}}
\newcommand{\G}[1]{G^{(#1)}}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tpsi}{\tilde{\psi}}

@@

The main tool to understand linear system game is through its solution group over $\Z_d$.
\begin{definition}[Solution group over $\Z_d$ \cite{coladan2017}]
	For the linear system game associated with $Ax = b$ over $\Z_d$, its solution group $\Gamma(A,b,\Z_d)$ has 
	one generator for each variable and one relation for each equation and relations enforcing that the variables in the same
	equation commutes. The set of local commutativity relations is denoted by $R_c$ and defined by
	\begin{align}
		R_c := \set{ [x_i, x_j] |  A_{li} \neq 0 \neq A_{lj} \text{ for some } 1 \leq l \leq m}.
	\end{align}
	The set of constraint satisfaction relations is denoted by $R_{eq}$ and defined by.
	\begin{align}
		R_{eq} := \set{ \J^{-b(l)} \Pi_{i=1}^n  x_i^{A_{li}} | 1\leq l\leq m}
	\end{align}
	Then the solution group has presentation 
	\begin{align}
	\Gamma(A,b,\Z_d) := \ip{ \{x_i\}_{i=1}^n \cup \{\J\} : R_c \cup R_{eq} \cup \{ (x_i)^d, \J^d| 1 \leq i \leq n\}}. 
	\end{align}
\end{definition}
Note that the relations $(x_i)^d$ and $\J^d$ ensure that we have solutions over $\Z_d$.
Then the operator solution of $\Gamma(A,b,\Z_d)$ is given below.
\begin{definition}[Operator solution]
	An operator solution for the linear system game associated with $Ax =b$ over $\Z_d$ is a unitary representation
	$\tau$ of $\Gamma(A,b,\Z_d)$ such that $\tau(\J) = \omega_d\1$. A conjugate operator solution is a unitary 
	representation mapping $\J$ to $\overline{\omega_d}\1$.
\end{definition}
What has been established in Ref.\cite{cleve2017,coladan2017} is that we can construct a perfect strategy of a
linear system game from its operator solution and vice versa.
%========================================
\section{Components of $\G{d}$}
%========================================
Suppose we would like to self-test $\ket{\EPR{d}}$ with $\G{d}$, where $d$ is prime and has primitive root $2$.
Later we will see how to deal with general prime numbers and why there are infinitely many prime dimensional EPR pairs 
that can be self-tested by a variant of $\G{d}$.
%----------------------------------------------------------------
\subsection{The linear system game}
%----------------------------------------------------------------
The main component of $\G{d}$ is a linear system game $\LS$, whose solution group is derived from the qudit Pauli group,
which is defined as
\begin{align}
	\Pg_d = \langle x, z, \J : x^d = z^d = \J^d = e, zxz^{-1}x^{-1} = \J, x\J x^{-1}\J^{-1}= z\J z^{-1}\J^{-1} = e\rangle. 
\end{align}
The goal of our modification is to construct $\Pg_{\LS}$ which has implicit $d$-dependence.
We first introduce new generators $u_x$ and $u_z$ to $\Pg_d$, and replace the relation $x^d = z^d = e$ 
by the following relations
\begin{align}
\label{eq:sim}
	u_x x u_x = x^2, \quad
	u_z z u_z = z^2.
\end{align}
Consequently, the $d$ dependency of $\G{d}$ comes from constraints imposed by other components of the game,
\footnote{Figuring out what $a$ is will take us one step closer to resolving Artin's Conjecture\cite{murty1988}.}
but the alphabet sizes are determined by $\Pg_{\LS}$ and we will see why they are constant.
Next, we drop the relation $\J^d = e$ and make the value of $\J$ determined by $x$ and $z$ in the 
relation $xzx^{-1}z^{-1} = \J$.

It can be easily checked that $\paulix{d}$ and $\pauliz{d}$ can be extended to a representation of $\Pg_{\LS}$ 
where  $\paulix{d}$ and $\pauliz{d}$ are defined by
\begin{align}
	\paulix{d} = \sum_{i=0}^{d-1} \ketbra{i+1 \pmod{d} }{i}  \quad \quad
	\pauliz{d} = \sum_{i=0}^{d-1} \omega_d^i \ketbra{i}{i}.
\end{align}
Moreover, if $U_x\paulix{d}U_x^\dagger = (\paulix{d})^2$ and $U_z\pauliz{d}U_z^\dagger = (\pauliz{d})^2$,
we can verify that 
\begin{align}
	U_xU_z = \1 = U_zU_x,
\end{align}
Hence, we do not need both $u_x$ and $u_z$ as generators and we just need one of them.
In the end, we define $\Pg_{\LS}$ by
\begin{equation}
\begin{aligned}
	\Pg_{\LS} =  \langle x, z, u, \J :  &zxz^{-1}x^{-1} = \J, [x,\J]=[z,\J]=[u,\J] = e, \\
	&uxu^{-1} = x^2, u^{-1}zu = z^2 \rangle. 
\end{aligned}
\end{equation}
This group will be embedded in a solution group, $\Gamma(\LS)$, following Slofstra's embedding techniques.
The corresponding game $\LS$ has $n = 2351$ variables and $m= 1916$ equations.
See Appendix~\ref{sec:construct} for details.
%------------------------------------------------------------------------
\subsection{The extended weighted CHSH game}
%------------------------------------------------------------------------
The extended weighted CHSH game is added to make sure that some of Alice and Bob's observables have
eigenvalues $\omega_d$ and $\omega_d^{d-1}$.
The notation for the extended weighted CHSH game that enforces the eigenvalues of the observable $U$ is 
$\CHSH_U$, where the superscript $d$ means that the rules of this game depends on $d$.
Intuitively, this is one step towards verifying Alice and Bob use $\paulix{d}$ and $\pauliz{d}$ in their operator solution.

In this game, Alice and Bob each gets a question $x$,$y \in \{ 0, 1, \ast\}$ and 
they answer with $a,b \in \{0,1,\diamond,\perp\}$. 
The scoring rules are
\begin{itemize}
	\item \textbf{Case 1:} $x = y = \ast$, Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
	they score only if $a = b$;
	\item \textbf{Case 2a:} $x,y \in \{0,1\}$ and they answer with $a,b \in \{0,1\}$, then
	their answers are scored according to $I_{-\cot(\pi/2d)}$
	\item \textbf{Case 2b:} $x,y \in \{0,1\}$ and Alice answer with $\perp$, then all possible outputs from Bob
	are discarded;
	\item \textbf{Case 3:} $x \in {0,1}, y = \ast$, when Bob answers $\diamond$, Alice should answer with $\{0.1\}$ but not $\perp$,
	when Bob answers $\perp$ Alice should answer $\perp$ too;
	\item \textbf{Case 4:} other combination of inputs are not scored.
\end{itemize}
In the ideal strategy, Alice and Bob share the state $\ket{\psi} =1/\sqrt{d} \sum_{i=0}^{d-1} \ket{u_i}\ket{u_i}$.
We define two subspaces $V = \spn\{\ket{u_1}, \ket{u_{d-1}}\}$ and $V^\perp = \C^d \setminus\spn\{\ket{u_1}, \ket{u_{d-1}}\}$ amd
define $\Pi_V$ and $\Pi_{V}^\perp$ to be the corresponding projectors. Note that $V$ is the subspace on which they should
 maximaize $\langle I_{-\cot(\pi/2d)} \rangle$.

We summarize the projectors of the ideal strategy and the ideal correlation in the following two charts.
Note that we don't explicitly calculate the conditional probabilities of the form $\pr{\perp 0}{xy}$ because they are irrelevant
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{2}{|c|}{$x=\ast$}\\
\cline{3-4}
\multicolumn{2}{|c|}{} &$a = \diamond$ & $a = \perp$ \\
\hline
\hline
\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & 2/d & 0 \\
\cline{2-4}
&$b=\perp$ & 0 & (d-2)/d \\
\hline
\end{tabular}
\caption{Alice and Bob's behaviour when $x=y=\ast$.}
\end{center}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{3}{|c|}{$x=0$}&
\multicolumn{3}{|c|}{$x=1$} \\
\cline{3-8}
\multicolumn{2}{|c|}{} &
$a = 0$ & $a=1$ & $a=\perp$ &
$a = 0$ & $a=1$ & $a=\perp$\\
\hline
\hline
\multirow{2}{*}{$y = 0$} & $b=0$ & $\frac{\cos^2(\pi/4d)}{d}$ & $\frac{\sin^2(\pi/4d)}{d}$ & \small $\pr{\perp0}{00}$ 
& $\frac{1+\sin(\pi/2d)}{2d}$ & $\frac{1-\sin(\pi/2d)}{2d}$ & \small  $\pr{\perp0}{10}$ \\
\cline{2-8}
&$b=1$ & $\frac{\sin^2(\pi/4d)}{d}$ & $\frac{\cos^2(\pi/4d)}{d}$ & $\frac{d-2}{d}-\pr{\perp0}{00}$ 
&  $\frac{1-\sin(\pi/2d)}{2d}$ & $\frac{1+\sin(\pi/2d)}{2d}$ & \small $\frac{d-2}{d} - \pr{\perp0}{10}$  \\
\hline
\multirow{2}{*}{$y = 1$} & $b=0$ & $\frac{\cos^2(\pi/4d)}{d}$ & $\frac{\sin^2(\pi/4d)}{d}$ & \small $\pr{\perp0}{01}$ & 
$ \frac{1-\sin(\pi/2d)}{2d}$ & $ \frac{1+\sin(\pi/2d)}{2d}$ & \small $\pr{\perp 0}{11}$  \\
\cline{2-8}
&$b=1$ & $\frac{\sin^2(\pi/4d)}{d}$ & $\frac{\cos^2(\pi/4d)}{d}$ & \small $\frac{d-2}{d}-\pr{\perp0}{01}$ &  
$ \frac{1+\sin(\pi/2d)}{2d}$ & $ \frac{1-\sin(\pi/2d)}{2d}$ & \small $\frac{d-2}{d}- \pr{\perp 0}{11}$ \\
\hline
\end{tabular}
\end{center}
\caption{Alice and Bob's behaviour when $x,y \in [2]$.}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{3}{|c|}{$x=0$}&
\multicolumn{3}{|c|}{$x=1$} \\
\cline{3-8}
\multicolumn{2}{|c|}{} &
$a = 0$ & $a=1$ & $a=\perp$ &
$a = 0$ & $a=1$ & $a=\perp$\\
\hline
\hline
\multirow{2}{*}{$y = \ast$} & $b=\diamond$ & $1/d$ & $1/d$ & 0 
& $1/d$ & $1/d$ & 0 \\
\cline{2-8}
&$b=\perp$ & 0 & 0 & $\frac{d-2}{d}$ 
&  0 & 0 & \small $\frac{d-2}{d} $  \\
\hline
\end{tabular}
\end{center}
\caption{Alice and Bob's behaviour when $x\in [2]$ and $y = \ast$.}
\end{table}
Alice's projectors are 
\begin{align*}
	&A_\ast^\diamond = \Pi_V, A_\ast^\perp = \Pi_V^\perp \\
	&A_0^0 = \ketbra{u_1}{u_1}, A_0^1 = \ketbra{u_{d-1}}{u_{d-1}}, A_0^\perp = \Pi_V^\perp\\
	&A_1^0 = \frac{1}{2}(\ket{u_1}+\ket{u_{d-1}})(\bra{u_1}+\bra{u_{d-1}}), 
	A_0^1 = \frac{1}{2}(\ket{u_1}-\ket{u_{d-1}})(\bra{u_1}-\bra{u_{d-1}}),A_0^\perp = \Pi_V^\perp
\end{align*}
Bob's projectors are 
\begin{align*}
	&B_\ast^\diamond = \Pi_V, B_\ast^\perp = \Pi_V^\perp \\
	&B_0^0|_V = \left( \cos(\frac{\pi}{4d})\ket{u_1} + \sin(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \cos(\frac{\pi}{4d})\bra{u_1} + \sin(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
	&B_0^1|_V = \left( \sin(\frac{\pi}{4d})\ket{u_1} - \cos(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \sin(\frac{\pi}{4d})\bra{u_1} - \cos(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
	&B_1^0|_V = \left( \cos(\frac{\pi}{4d})\ket{u_1} - \sin(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \cos(\frac{\pi}{4d})\bra{u_1} - \sin(\frac{\pi}{4d})\bra{u_{d-1}}\right)\\
	&B_0^1|_V = \left( \sin(\frac{\pi}{4d})\ket{u_1} + \cos(\frac{\pi}{4d})\ket{u_{d-1}}\right)
	\left( \sin(\frac{\pi}{4d})\bra{u_1} + \cos(\frac{\pi}{4d})\bra{u_{d-1}}\right).
\end{align*}
About Bob's projectors for input $y \in [2]$, we are only interested in their actions when restricted 
to the subspace $V$. Their actions on the subspace $V^\perp$ is irrelevant in this game.

The importance of this game is summarized in the following lemma.
\begin{lemma}
	\label{lm:chsh_comp}
	Suppose a quantum strategy $\left(\{\{\tA_x^a\}_a\}_x, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}\right)$
	achieves the optimal correlation of $\CHSH$, then there exists unitaries $U_A$ and $U_B$ 
	such that 
	\begin{align*}
		&U_A\x U_B \left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) = \ket{\EPR{2}} \\
		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 + \tB_1}{2\cos(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
		=\1 \x \pauliz{2} \ket{\EPR{2}} \\
		&U_A\x U_B \left[\left(\1 \x  \frac{\tB_0 - \tB_1}{-2\sin(\pi/2d)}\right)\left(\tA_\ast^\diamond \x \tB_\ast^\diamond \ket{\tpsi}\right) \right]
		=\1 \x \paulix{2} \ket{\EPR{2}} 
	\end{align*}
	where $\tB_0 = \tB_0^0 - \tB_0^1$ and $\tB_1 = \tB_1^0 - \tB_1^1$.
\end{lemma}
\begin{proof}
Note that $\tA_x^a \tB_y^b$ means $\tA_x^a \x \tB_y^b$ in the following proof.

From the marginal distribution $\pb{\diamond}{\ast} = \pa{0}{0}+\pa{1}{0} = 2/d$,
we know $\| \tB_\ast^\diamond \ket{\tpsi} \| = \| (\tA_0^0+\tA_0^1) \ket{\tpsi}\| = \sqrt{2/d}$.
Since $\pr{0\diamond}{0\ast} + \pr{1\diamond}{0\ast} = 2/d$, we find that 
\begin{align*}
	\frac{\bra{\tpsi}\tB_\ast^\diamond (\tA_0^0+\tA_0^1) \tB_\ast^\diamond\ket{\tpsi}}{ \| \tB_\ast^\diamond \ket{\tpsi} \|^2} = 1,
\end{align*}
which means that 
\begin{align}
	(\tA_0^0+\tA_0^1)\tB_\ast^\diamond \ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}.
\end{align}
Using the commutation relation between $(\tA_0^0+\tA_0^1)$ and $\tB_\ast^\diamond$, we get
\begin{align*}
	\frac{\bra{\tpsi} (\tA_0^0+\tA_0^1) \tB_\ast^\diamond(\tA_0^0+\tA_0^1)\ket{\tpsi}}{ \| (\tA_0^0+\tA_0^1) \ket{\tpsi} \|^2} = 1,
\end{align*}
Similar argument gives us that 
\begin{align}
	\tB_\ast^\diamond (\tA_0^0+\tA_0^1) \ket{\tpsi} = (\tA_0^0+\tA_0^1)\ket{\tpsi}.
\end{align}
The two equations above can be chained by commutativity to reach the conclusion that 
\begin{align}
	(\tA_0^0+\tA_0^1)\ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}.
\end{align}
Following the same line of argument, we can conclude that
\begin{align}
	\tB_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \ket{\tpsi} = (\tA_0^0+\tA_0^1)\ket{\tpsi} = (\tA_1^0+\tA_1^1)\ket{\tpsi}.
\end{align}
Looking at the marginal distribution when Alice and Bob output $\perp$, we conclude that 
\begin{align}
	\tB_\ast^\perp \ket{\tpsi} = \tA_\ast^\perp \ket{\tpsi} = \tA_0^\perp \ket{\tpsi} = \tA_1^\perp \ket{\tpsi},
\end{align}
with similar arguments.

Next we examine the CHSH-type correlation when $x,y \in [2]$,
\begin{align*}
	   \bra{\tpsi} \tA_0^0\tB_0^0 \ket{\tpsi} 
	= &\bra{\tpsi}(\tA_\ast^\diamond + \tA_\ast^\perp) \tA_0^0\tB_0^0 (\tA_\ast^\diamond + \tA_\ast^\perp)\ket{\tpsi} \\
	= & \bra{\tpsi}\tA_\ast^\diamond \tA_0^0\tB_0^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\diamond \tA_0^0\tB_0^0 \tA_\ast^\perp\ket{\tpsi} \\
	&+\bra{\tpsi}\tA_\ast^\perp \tA_0^0\tB_0^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\perp \tA_0^0\tB_0^0 \tA_\ast^\perp\ket{\tpsi}\\
	= & \bra{\tpsi}\tB_\ast^\diamond \tA_0^0\tB_0^0 \tB_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_\ast^\diamond \tA_0^0\tB_0^0 \tA_0^\perp\ket{\tpsi} \\
	&+\bra{\tpsi}\tA_0^\perp \tA_0^0\tB_0^0 \tA_\ast^\diamond\ket{\tpsi} + \bra{\tpsi}\tA_0^\perp \tA_0^0\tB_0^0 \tA_0^\perp\ket{\tpsi}\\
	=&\bra{\tpsi}\tB_\ast^\diamond \tA_0^0\tB_0^0 \tB_\ast^\diamond\ket{\tpsi},
\end{align*}
where we use the facts that $\tB_\ast^\diamond \ket{\tpsi} = \tA_\ast^\diamond \ket{\tpsi}$, $\tA_\ast^\perp \ket{\tpsi} = \tA_0^\perp \ket{\tpsi}$ and that 
$\spn(\tA_0^0) \cap \spn(\tA_0^\perp) = \emptyset$. 
This means that if Alice and Bob share the state $\tB_\ast^\diamond \ket{\tpsi}/\|\tB_\ast^\diamond \ket{\tpsi}\|$ and apply 
$\tA_0^0\tB_0^0$, the conditional probability is
\begin{align}
	\frac{\bra{\tpsi}\tB_\ast^\diamond \tA_0^0\tB_0^0 \tB_\ast^\diamond\ket{\tpsi}}{\bra{\tpsi} \tB_\ast^\diamond \tB_\ast^\diamond \ket{\tpsi}} = \frac{\cos^2(\pi/4d)}{2}.
\end{align} 
We can re-normalize the other correlations of $a,b \in [2]$ when $x,y \in [2]$ similarly and get a new set of correlations 
which achieves the maximal value of $\langle \1_{-\cot(\pi/2d)}\rangle$. 
The conclusion of \cref{lm:chsh_comp} follows the application of \cref{thm:selftest} on the state $\tA_\ast^\diamond\tB_\ast^\diamond \ket{\tpsi}/\|\tA_\ast^\diamond\tB_\ast^\diamond \ket{\tpsi}\|$ as $\tA_\ast^\diamond\tB_\ast^\diamond \ket{\tpsi} = \tB_\ast^\diamond \ket{\tpsi}$.
\end{proof}
Note that the combination of \cref{lm:chsh_comp} with \cref{prop:2d-subspace} gives us that 
$\tB_0\tB_1$ has eigenvalues $\omega_d$ and $\omega_d^{-1}$.

%------------------------------------------------------------------------
\subsection{The single value test}
%------------------------------------------------------------------------
By the following test, we want to make sure that some unitary $U$ has eigenvalue $1$.
In this test $X = \{\ast\}$, $Y = \{0,1,\ast\}$, $A = \{\diamond, \perp\}$ and $B = \{0,1, \diamond, \perp\}$.
The scoring rules are
\begin{itemize}
	\item \textbf{Case 1} $x = y = \ast$: Alice and Bob should answer with $a, b \in \{\diamond, \perp\}$ and 
	they score only if $a = b$;
	\item \textbf{Case 2} $x =\ast$ and $y = 0$: when Alice answer $\diamond$, Bob should answer $0$, when 
	Alice answer$\perp$ all answers of Bob are accepted;
	\item \textbf{Case 3} $x = \ast$ and $y = 1$: when Alice answer $\diamond$, Bob should answer $0$, when 
	Alice answer$\perp$ all answers of Bob are accepted.
\end{itemize}

Define the subspace $V = \spn\{ \ket{u_0} \}$.
The ideal strategy has projective measurement 
\begin{align*}
&A_\ast^\diamond = B_\ast^\diamond= \ketbra{u_0}{u_0}, 
&&A_\ast^\perp = B_\ast^\perp = \1 - \ketbra{u_0}{u_0},\\
&B_0^0|_V = B_1^0|_V = \ketbra{u_0}{u_0}, 
&&B_0^1|_V = B_1^1|_V = 0.
\end{align*}
The shared state is 
\begin{align}
	\ket{\psi} = \frac{1}{\sqrt{d}} \sum_{i \in [d]} \ket{u_i}\ket{u_i}.
\end{align}
Note that the shared state is the same as the one used in the extended weighted CHSH game.
So are the observables $B_0$ and $B_1$.

It is easy to calculate the ideal correlation, which is
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c|}{} &
\multicolumn{2}{|c|}{$y=\ast$} &
\multicolumn{2}{|c|}{$y=0$} &
\multicolumn{2}{|c|}{$y=1$}\\
\cline{3-8}
\multicolumn{2}{|c|}{} &$b = \diamond$ & $b = \perp$ & $b = 0$ & $b = 1$ & $b = 0$ & $b = 1$\\
\hline
\hline
\multirow{2}{*}{$x = \ast$} & $a=\diamond$ & $1/d$ & 0 & $1/d$ & 0 & $1/d$ & 0 \\
\cline{2-8}
&$a=\perp$ & 0 & $(d-1)/d$ & \small $\pr{\perp0}{\ast0}$ & \small $\frac{d-1}{d} -\pr{\perp0}{\ast0}$  
& \small $\pr{\perp0}{\ast1}$ & \small $\frac{d-1}{d}- \pr{\perp0}{\ast0}$  \\
\hline
\end{tabular}
\caption{Ideal correlation of the single value test.}
\end{center}
\end{table}
The reason we have $y=0$ or $y=1$ is that we want Bob to reuse operators from $\LS$ and we want to
conclude that $B_0B_1$ has eigenvalue $1$.

\begin{lemma}
	\label{lm:svt_comp}
	If a quantum strategy$(\{\tA_\ast^a\}_a, \{\{\tB_y^b\}_b\}_y, \ket{\tpsi}$ has the same behaviour as
	the optimal one, then $(\tB_0^0 - \tB_0^1)(\tB_1^0-\tB_1^1)$ has eigenvalue $1$.
\end{lemma}
\begin{proof}
By the marginal distribution we know that $\| A_\ast^\diamond \ket{\psi}\| = \frac{1}{\sqrt{d}}$.
From the condition that $P(\diamond 0|\ast 0) = 1/d$, we know
\begin{align}
	\frac{  \bra{\psi} \tA_\ast^\diamond  \tB_0^0 \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|^2} = 1,
\end{align}
which implies that 
\begin{align}
 \tB_0^0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
\end{align}
With similar reasoning, we get
\begin{align}
 \tB_1^0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
\end{align}
Hence $ \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} $ is in the intersection of $\supp(\tB_0^0)$ and $\supp(\tB_1^0)$.
Since $\supp(\tB_y^0)$ and $\supp(\tB_y^1)$ are disjoint, we know
\begin{align*}
	(\tB_y^0 - \tB_y^1)  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}  =  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} - 0 = \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} 
\end{align*}
for $y = 0,1$.
Therefor, we know $ \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} $ is an eigenvector of $\tB_0\tB_1$ with eigenvalue $1$ because
\begin{align}
	\tB_0\tB_1 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} = \tB_0 \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|} =  \frac{\tA_\ast^\diamond \ket{\psi}}{\| \tA_\ast^\diamond \ket{\psi}\|}.
\end{align}
\end{proof}
In the later section, when we apply this test to make sure some unitary $U$ has eigenvalue $1$, 
we denote the test by $\SVT_U$.

\bibliographystyle{alphaurl}
\bibliography{quantum_correlation}
\appendix
%========================================
\section{Proof of \cref{thm:selftest} }
\label{sec:selftest}
%========================================
\begin{proof}
Following the techniques developed in Ref.~\cite{bamps2015}, the first step is to find a sum-of-square decomposition of 
\begin{align}
	\bar{\I}_\alpha = 2\sqrt{\alpha^2+1} \1 - \I_\alpha
	= \frac{2}{\sin(\mu)} \1 - \frac{\cos(\mu)}{\sin(\mu)}(A_0B_0+A_0B_1) -  A_1B_0 + A_1B_1.
\end{align} 
With the following notation
\begin{align*}
	Z_A = A_0 &\quad X_A = A_1\\
	Z_B = \frac{B_0+B_1}{2\cos(\mu)} &\quad X_B = \frac{B_0-B_1}{2\sin(\mu)},
\end{align*}
the two SOS decompositions that we use are
\begin{align}
	\label{eq:sos1}&\bar{\I}_\alpha = \frac{\sin(\mu)\bar{\I}_\alpha^2 + 4\sin(\mu)\cos(\mu)^2(Z_AX_B+X_AZ_B)^2}{4},\\
	\label{eq:sos2}&\bar{\I}_\alpha = \frac{\cos^2(\mu)}{\sin(\mu)}(Z_A-Z_B)^2 + \sin(\mu) (X_A-X_B)^2.
\end{align}
The verification is omitted here.
